Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-12-17 Manuscript/manuscript.tex
Small improvemnets in Methods: Electronic continuum correction for PS lipids (just this small section)

The lack of electronic polarizability has been a concern since the
early days of classical MD simulations of lipids \cite{jonsson86,egberts94, berendsen1996},
where the atomic charges were scaled by a factor of 1/2 to effectively
include the electrostatic screening from the missing electronic polarizability.
The electronic continuum correction (ECC) is a more sophisticated version of the charge scaling.

The polarization of electrons in ECC-lipids uses the implicit method termed electronic continuum correction (ECC). \cite{leontyev09, Pluharova2014, martinek17, melcr18} 
In this method, a system of polarizable particles is represented with an equivalent system of particles with fixed charges. 
This is practically achieved rescaling the charges with a pre-determined scaling factor, $f_q$,
which is derived from the high-frequency dielectric constant of electrons, $\epsilon_{el}$, as
-OR-
In ECC, the charges are rescaled with a pre-determined scaling factor, $f_q$,
\begin{equation}
  f_q = \frac{1}{\sqrt{\epsilon_{el}}} ,
\end{equation}
where $\epsilon_{el}$ is the high-frequency dielectric constant of electrons.
The value of $\epsilon_{el} = 1.78$ for water solutions gives the scaling
factor of $f_q \approx 0.75$ for aquaeous environments \cite{leontyev09}.
This has been recently applied to improve classical models for ions and
other biomolecules \cite{Pluharova2014, martinek17, melcr18}
\todo{Pavel can probably update this}.

Recently we applied the ECC also to the Amber based lipid14 force field \cite{dickson14} to
improve the cation binding affinity to zwitterionic POPC lipid bilayers \cite{melcr18}.
In contrast to the total charge of ions, the partial charges in force fields of zwitterionic
depend on the methods used to derive the force field which may already partially include the
electronic polarizability effects. Therefore, the optimal scaling factor for charges in
zwitterionic lipids may be larger than the theoretically derived $f_q \approx 0.75$.
In the recent work, we found optimal results for cation binding affinity and
bilayer structural properties when the partial charges and Lennard-Jones $\sigma$
parameters of headgroup, glycerol backbone, and carbonyl regions of the lipid14 POPC model
were scaled with the factors of $f_q = 0.8$ and $f_\sigma = 0.89$, respectively \cite{melcr18}.

Here, we apply the ECC to the Amber based lipid17 parameters \cite{lipid17-future} of POPS lipid with
a total monovalent negative charge. In this case we apply the scaling factor of $f_q = 0.75$ 
also to the lipid because it carries a physical total charge similar to the ions in solution and
the lipid charges has to neutralize the counterion charges in simulations.
For the Lennard-Jones $\sigma$ parameters, we used the same scaling factor of $f_\sigma = 0.89$
as in the ECC-POPC model \cite{melcr18}.
%we used exactly the pre-determined scaling factor 
%to represent the effects of electronic polarization
%yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}
Similarly to the ECC-POPC model \cite{melcr18}, we applied the ECC only to the
headgroup, glycerol backbone, and carbonyl regions.
%polar parts of the phospholipid,
%i.e., charges on all atoms except on alkyl tails, 
%which do not encounter direct contacts with ions.

>>>>

\todo{Joe: this paragraph requires editing.}
The lack of electronic polarizability has been a concern since the
early days of classical MD simulations of lipids \cite{jonsson86,egberts94, berendsen1996},
where the atomic charges were scaled by a factor of 1/2 to effectively
include the electrostatic screening from the missing electronic polarizability.
The electronic continuum correction (ECC) is a more sophisticated version of the charge scaling.

The polarization of electrons in ECC-lipids uses the implicit method termed electronic continuum correction (ECC). \cite{leontyev09, Pluharova2014, martinek17, melcr18} 
In this method, a system of polarizable particles is represented 
with an equivalent system of particles with fixed charges,
which account for the electronic polarizability \emph{implicitly}. 
This is practically achieved by rescaling the charges with a pre-determined scaling factor, $f_q$,
which is derived from the high-frequency dielectric constant of electrons, $\epsilon_{el}$, as
\begin{equation}
  f_q = \frac{1}{\sqrt{\epsilon_{el}}} ,
\end{equation}
The value of $\epsilon_{el} = 1.78$ for water solutions gives the scaling
factor of $f_q \approx 0.75$ for aquaeous environments \cite{leontyev09}.
This has been recently applied to improve classical models for ions and
other biomolecules \cite{Pluharova2014, martinek17, melcr18}
\todo{Pavel can probably update this (insulin?)}.

Recently we applied the ECC also to the Amber based lipid14 force field \cite{dickson14} to
improve the cation binding affinity to zwitterionic POPC lipid bilayers \cite{melcr18}.
In contrast to the total charge of ions, 
the partial charges in force fields of zwitterionic molecules
depend on the methods used to derive the force field, 
which may already partially include the
electronic polarizability effects. Therefore, the optimal scaling factor for charges in
zwitterionic lipids may vary from (be even larger) than the theoretically derived $f_q \approx 0.75$.
In the recent work, we found optimal results for cation binding affinity and
bilayer structural properties when the partial charges and Lennard-Jones~$\sigma$
parameters of all non-tail atoms of the lipid14 POPC model
(i.e., headgroup, glycerol backbone, and carbonyl regions) 
were scaled with the factors $f_q = 0.8$ and $f_\sigma = 0.89$  \cite{melcr18}.

Here, we apply the ECC to the Amber based lipid17 parameters \cite{lipid17-future} of POPS lipid with
a total monovalent negative charge. 
In this case we treat the POPS lipids like ions
applying to it the scaling factor of $f_q = 0.75$,
as it carries a physical total charge similar to the ions in solution, 
and the lipid charges has to neutralize the counterion charges in simulations.
For the Lennard-Jones~$\sigma$ parameters, we used the same scaling factor of $f_\sigma = 0.89$
as in the ECC-POPC model \cite{melcr18}.
%we used exactly the pre-determined scaling factor 
%to represent the effects of electronic polarization
%yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}
Similarly to the ECC-POPC model \cite{melcr18}, we applied the ECC only to the
non-tail atoms, i.e., to atoms in the headgroup, glycerol backbone, and carbonyl regions. 
%polar parts of the phospholipid,
%i.e., charges on all atoms except on alkyl tails, 
%which do not encounter direct contacts with ions.
